A successful observational test of black hole and galaxy co-evolution models since $z\sim1.7$

### 2020-01-30 QSOII_paper/ApJ_manuscript/manuscript.tex
Update manuscript.tex

\pink{
\section{Sample: Observation and Simulation}~\label{sec:sample}
% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
In this section, we introduce the comparison samples of the scaling relations, using the observed data (Section~\ref{hst_sample}) and the predicted ones using two independent numerical simulations (Section~\ref{sample_sim}).}

>>>>

\pink{
\section{Sample: Observation and Simulation}~\label{sec:sample}
% The work that we want to do
	%Sample selection
	%The advantage of our measurements
	%Compare to which simulation? (some introduction)
	%Any expectation?
	%mention the scatter.
In this section, we introduce our comparison samples, including the observed scaling relations (Section~\ref{hst_sample}) and the predicted ones by two independent numerical simulations (Section~\ref{sample_sim}).}
